\begin{abstract}
The 2020 MOSAR (MOdular Spacecraft Assembly and Reconfiguration) project was initiated to develop innovative technologies aimed at standardising satellites and components by raising the degree of space system modularity. As part of the project, a ground demonstrator for on-orbit modular and reconfigurable satellites was created, consisting of reusable spacecraft modules and a repositionable symmetric walking robotic manipulator. This demonstrator can execute basic instructions to relocate the manipulator and move modules between positions. However, these instructions are currently generated and verified manually before transmission to the demonstrator.
\\
In this project we develop a reconfiguration planning system to autonomously generate instructions for reconfiguring modular spacecraft. Despite the limited research in this field, we demonstrate the feasibility of developing a reliable reconfiguration planner that considers the physical constraints introduced by the mobile manipulator and local environment. This was achieved by dividing the discrete and continuous components of the reconfiguration planner into two separate systems that communicate through feedback strategies in a control-loop mechanism. Our results show the system's capability to solve complex reconfiguration problems and identifies areas for further development.
\\
This project serves as a foundation for developing more advanced systems with enhanced capabilities, potentially benefiting the space industry in the assembly and reconfiguration of modular space systems.
\end{abstract}