\subsection{Feedback Strategies}
Without feedback strategies, the system can find a step-by-step solution to reconfigure modules into the desired goal configuration and verify whether the mobile manipulator can execute the semantic solution. If the mobile manipulator cannot execute the solution, the system fails in its current state.
\\\\
Feedback Strategies establish a control loop that facilitate communication between the logic and physical layers, enabling them to collaborate towards finding solutions that meet their respective goals. While various feedback strategies were considered, the project focuses on implementing those related to final output validation rather than computation time optimization. However, strategies for both aspects were explored in case of early project completion or for future work beyond the project's scope.

\subsubsection{Semantic Solution Verification}
The primary feedback strategy implemented in this project involves simple verification of semantic solutions. Failed solutions are returned to the logic layer, and the problematic transition is removed from the search tree, along with all associated states. The logic layer then continues the search. There is concern that early failures in the physical layer may significantly reduce the search space, potentially hindering the discovery of reasonable solutions. Further testing and research are needed to address this issue and refine the feedback strategy.

\subsubsection{Failure Memory}
Although implementing a failure memory, like the one developed in previous work \cite{9438257}, was considered, it was deemed beyond the project's scope due to its primary focus on time performance. The failure memory utilises a machine learning algorithm to predict physical layer failures based on past data, optimizing the system's runtime by reducing failures. Incorporating a failure memory would provide the system with scalability over time with the collection of failure data, enabling it to generate solutions for larger systems in a reasonable timeframe. Though currently it is unsuitable for space applications due to the reliance on black box machine learning algorithms.  